The growth of children's semantic and phonological networks: insight from 10 languages

### 2020-04-02 journal/ms.Rmd
final revisins

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(ggpubr)
library(knitr)
library(boot)
library(dplyr)
library(gridExtra)
library(langcog)
library(ggthemes)
library(broom)
library(HDInterval)
library(kableExtra)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

plot_correlation_prod_1 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_prod_2 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

plot_correlation_comp_1 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_comp_2 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

powerProd <- powerL %>%
  dplyr::filter(measure == 'produces') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  spread(domain, data) %>%
  unnest(.sep = "_")

powerComp <- powerL %>%
  dplyr::filter(measure == 'understands') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  spread(domain, data) %>%
  unnest(.sep = "_")

@@

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

>>>>

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(ggpubr)
library(knitr)
library(boot)
library(dplyr)
library(gridExtra)
#library(langcog)
library(ggthemes)
library(broom)
library(HDInterval)
library(kableExtra)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

@@

plot_correlation_prod_1 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_prod_2 <- ggplot(subset(data_long, measure == "produces" & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

plot_correlation_comp_1 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_comp_2 <- ggplot(subset(data_long, measure == "understands" & aoa < 35 & data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ predictor)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands" & correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

powerProd <- powerL %>%
  dplyr::filter(measure == 'produces') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  pivot_wider(names_from = domain, values_from = data) %>%
  #spread(domain, data) %>%
  unnest(names_sep = "_", cols = c(Phono, Sem))

powerComp <- powerL %>%
  dplyr::filter(measure == 'understands') %>%
  select(-measure) %>%
  group_by(language, domain) %>%
  nest() %>%
  pivot_wider(names_from = domain, values_from = data) %>%
  unnest(names_sep = "_", cols = c(Phono, Sem))

@@

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

@@

plot_correlation_1 <- ggplot(subset(data_long, data_long$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), 
                                  aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, correlations$language %in% c('Croatian', 'Danish', 'English', 'French','Italian')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")

plot_correlation_2 <- ggplot(subset(data_long,  data_long$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(x=value, y=aoa))+
  facet_grid(language~ measure)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  #coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations,  correlations$language %in% c('Norwegian', 'Russian', 'Spanish', 'Swedish','Turkish')), aes(label=paste("r=", cor, sep="")), x=1.5, y=35, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age (in months)")
